Argennon: A Scalable Cloud Based Smart Contract Platform

### 2022-08-07 tex/A.tex
changed chapter 1 of whitepaper some more

\begin{document}
    \maketitle
    \begin{abstract}
        Argennon is a next generation cloud based blockchain and smart
        contract platform. The Argennon blockchain uses
        a hybrid proof of stake (HPoS) consensus protocol, which is capable of combining the benefits of
        a centralized and a decentralized system. In Argennon, ledger storage and transaction processing are
        outsourced to the Argennon cloud and normal personal computers or smartphones, with limited hardware
        capabilities, can validate transactions and actively
        participate in the consensus protocol. This property makes Argennon a truly decentralized and
        democratic blockchain and one of the most secure existing platforms.

@@

        This set up allows for very high transaction throughput while at the same time remaining highly secure. The network 
        stays safe as long as at least one delegate and at least 1/3 of the validators in all validator assemblies remain honest.
    \end{abstract}
    \tableofcontents

>>>>

\begin{document}
    \maketitle
    \begin{abstract}
        Argennon is a next generation cloud based blockchain and smart
        contract platform. The Argennon blockchain uses
        a hybrid proof of stake (HPoS) consensus protocol, which is capable of combining the benefits of
        a centralized and a decentralized system. In Argennon, ledger storage and transaction processing are
        outsourced to the Argennon cloud while normal personal computers or smartphones, with limited hardware
        capabilities, can validate transactions and actively participate in the consensus protocol.

@@

        These properties make it possible for Argennon to achieve very high transaction throughput while requiring no trust
        in central parties.  
    \end{abstract}
    \tableofcontents
